\section{Bibliography}
\begin{thebibliography}{100}
\bibitem{DSC10}
Marek Krzysztof Misztal, \emph{Deformable Simplicial Complexes},
IMM-PHD-2010-241, DTU, Kongens Lyngby, 2010.


\bibitem{wikisc}
Wikipedia.org, \emph{Simplicial Complex},
\myurl{http://en.wikipedia.org/wiki/Simplicial_complex}, as it was in 2013.


\bibitem{rc09}
Robert Crandall, \emph{Image Segmentation Using the Chan-Vese Algorithm},
ECE 532 Project, 2009.


\bibitem{me13}
Martin Elvers, \emph{Mesh Based Control of Commercial Particle Fluid Simulators},
Master Thesis, Institute of Computer Science, Copenhagen Univeristy, 2013.


\bibitem{api13}
Autodesk Inc, \emph{Autodesk Maya 2013 API Documentation},
\myurl{http://docs.autodesk.com/MayaUL/2013/ENU/Maya-API-Documentation/index.html},
as it was in 2013.

\bibitem{Mayareq}
Autodesk Inc, \emph{Autodesk Maya 2013 API Documentation: Compiler Requirements},
\myurl{http://docs.autodesk.com/MayaUL/2013/ENU/Maya-API-Documentation/files/Setting_up_your_build_environment_Compiler_Requirements.htm},
as it was in 2013.

\bibitem{wikils}
Wikipedia.org, \emph{Laplacian smoothing},
\myurl{http://http://en.wikipedia.org/wiki/Laplacian_smoothing}, as it was in 2013

\bibitem{chanveseposter}
Bonde, Misztal, Erleben, Darkner, \emph{Image Segmentation using Moving Tetrahedral Meshes},
Poster by DIKU's image group, 2013.

\bibitem{cv01}
Chan, T. F. and L. A. Vese, \emph{Active Contours Without Edges}, Image Processing
IEEE Transactions on 10(2), 266–277, 2001.

\end{thebibliography}
